

```{r outlier-full}
print(df)
mod.full <- glm(heart_disease ~ ., data = df, family = 'binomial')
cooksd <- cooks.distance(mod.full)

print(mod.full)
anova(mod.full)
(summary((mod.full)))

fluidPage(
  titlePanel("Detecting Outiers with Cooks Distance"),
  mainPanel(
    h5("Fitting the full model and testing outliers."),
    tabsetPanel(
      tabPanel("Construct Full Model", htmlOutput("cfm")),
      tabPanel(
        "Outlier Detection",
        fluidRow(
          column(
            12,
            inputPanel(
              sliderInput("od_adjust", label = "Standard Deviations for Cooks Distance:", min = 0, max = 5, value = 3, step = 0.5)
            )
          ),
          column(
            12,
            plotOutput("cfmPlot")
          )
        )
      )
    )
  )
)

output$cfm <- renderUI({
  req(print(summary(mod.full), method = 'render'))
})
output$cfmPlot <- renderPlot({
  plot(cooksd,
     ylab = "Standard Deviation", 
     main = "Outlier Detection Method Reduced Model")
  abline(h = input$od_adjust*mean(cooksd), col = 'green')
})

#
#    counties %>% 
#      ggplot(aes(x = long, y = lat, group = group, fill = LnPopulationDensity)) +
#      coord_fixed(1.3) +
#      geom_polygon(color = 'white') +
#      geom_polygon(data=counties[counties$subregion == input$vcrPlot_selected,],
#                   color='red') +
#      theme_bw()
#  })
#
#
#
#  output$vcrPlot = renderggiraph({
#    plt = ggplot(pop.data[pop.data$Year == input$year, ]) +
#      geom_smooth(method = 'lm', aes(x = LnPopulationDensity, y = Violent.Crime.Rate)) +
#      geom_point_interactive(aes(x = LnPopulationDensity,
#                                 y = Violent.Crime.Rate,
#                                 size = MedianHousehold,
#                                 fill = established,
#                                 tooltip = subregion,
#                                 data_id = subregion),
#                             pch = 21) +
#     theme_bw() +
#     labs(x = 'Ln Population Density',
#          y = 'Violent Crime Rate (per 100k)', 
#          fill = 'Established') +
#      xlim(c(0, 8)) +
#      ylim(c(0, 800))
#    x = girafe(code = print(plt))
#    girafe_options(x, opts_selection(type='single'))
#  })

```


### Test Outliers
#### Construct Full Model
#     ```{r echo=FALSE}
#     mod.full <- aov(lm(heart_disease ~ ., data = df))
#     summary(mod.full)
#     ```
#     With the full model with outliers the factor for *Age* and *Cholestoral* do not appear to be a statistically significance.  
#     
#     #### Outlier Detection Methods **Cook's Distance**
#     ```{r}
#     cooksd <- cooks.distance(mod.full)
#     plot(cooksd,
#          ylab = "Standard Deviation",
#          main = "Outlier Detection Method Using Cooks Distance")
#     abline(h = 3*mean(cooksd), col = 'red')
#     ```
#     
#     #### Removing Outliers and Retesting Fit of Model
#     ```{r warning=FALSE}
#     outlier <- as.numeric(names(cooksd)[(cooksd > 3 * mean(cooksd, na.rm = TRUE))])
#     df %>% 
#       mutate(outlier = ifelse(rownames(df) %in% paste0("", outlier), TRUE, FALSE)) %>% 
#       filter(outlier == FALSE) %>% 
#       select(-outlier) -> df.no.outlier
#     mod.full.no.outlier <- aov(lm(heart_disease ~ ., data = df.no.outlier))
#     summary(mod.full.no.outlier)
#     ```
#     After removing the outliers using Cook's distance the factor for *Age* has some significant, but the factor for *Cholestoral* is doesn't seem to statistically significant.  
#     
#     #### Constructing Reduced Model without *Cholestoral*
#     ```{r}
#     df %>% 
#       select(-cholestoral) -> df.no.chol
#     mod.no.chol <- aov(lm(heart_disease ~ ., data = df.no.chol))
#     summary(mod.no.chol)
#     ```
#     When removing the factor for *Cholestoral* the significance for *Heart Disease* is decreased.  
#     
#     #### Outlier Detection Methods without *Cholestoral*
#     ```{r}
#     cooksd.no.chol <- cooks.distance(mod.no.chol)
#     plot(cooksd.no.chol,
#          ylab = "Standard Deviation", 
#          main = "Outlier Detection Method without Cholestoral")
#     abline(h = 3*mean(cooksd.no.chol), col = 'blue')
#     ```
#     
#     #### Removing Outliers and Retesting Fit of Model without *Cholestoral*
#     ```{r}
#     outlier = as.numeric(
#       names(cooksd.no.chol)[(cooksd.no.chol > 3 * mean(cooksd.no.chol, na.rm = TRUE))])
#     df.no.chol %>% 
#       mutate(outlier = ifelse(rownames(df.no.chol) %in% paste0("", outlier), TRUE, FALSE)) %>% 
#       filter(outlier == FALSE) %>% 
#       select(-outlier) -> df.no.chol.outlier
#     mod.no.chol.outlier <- aov(lm(heart_disease ~ ., data = df.no.chol.outlier))
#     summary(mod.no.chol.outlier)
#     ```
#     When removing *Cholestoral* and outliers the factor for *Resting Blood Pressure* is more significant, but *Heart Disease* is still less significant than the Full Model.
#     
#     #### Removing *Resting Blood Pressure* and *Cholestoral* in Reduced Model
#     ```{r warning=FALSE}
#     df %>% 
#       select(-cholestoral, -resting_bp) -> df.reduced
#     mod.reduced <- lm(heart_disease ~ ., data = df.reduced)
#     summary(mod.reduced)
#     ```
#     Moving to the reduced model, the factor for *Age* is less significant, and the intercept *Heart Disease* is no longer statistically significant.  
#     
#     #### Outlier Detection For Reduced Model
#     ```{r}
#     cooksd.reduced <- cooks.distance(mod.reduced)
#     plot(cooksd.reduced,
#          ylab = "Standard Deviation", 
#          main = "Outlier Detection Method Reduced Model")
#     abline(h = 3*mean(cooksd.reduced), col = 'green')
#     ```
#     
#     #### Removing Outliers and Retesting Fit of Reduced Model
#     ```{r}
#     outlier = as.numeric(
#       names(cooksd.reduced)[(cooksd.reduced > 3 * mean(cooksd.reduced, na.rm = TRUE))])
#     df.reduced %>% 
#       mutate(outlier = ifelse(rownames(df.reduced) %in% paste0("", outlier), TRUE, FALSE)) %>% 
#       filter(outlier == FALSE) %>% 
#       select(-outlier) -> df.reduced.no.outlier
#     mod.reduced.no.outlier <- lm(heart_disease ~ ., data = df.reduced.no.outlier)
#     summary(mod.reduced.no.outlier)
#     ```
#     After removing the outliers, the reduced model does show a marginal increase in *Heart Disease*, but *Heart Disease* is still less significant than the Full Model.
#     
#     
#     
#     
#     
#     
#     
#     
#     
#     
#     
#     
#     
#     
This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



