---
title: "STAT 806 Presentation"
subtitle: "Heart Disease Among Factors of Health, Exercise induced angina, Heart Rates, and Demographic Information"
author: "Jordan Winemiller"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r packages, include=FALSE}
ip = installed.packages()[, 1]
ip <- names(unlist(ip))

required_packages = c('remotes', 'shiny', 'ggplot2', 'tidyverse', 'dplyr', 'summarytools', 'ggiraph', 'DT', 'cowplot')
remote_packages = c('shinyaudio')
all_packages = c(required_packages, remote_packages)

for (package in all_packages) {
  if (package %in% ip) {
    next
  } else {
    if (package %in% remote_packages) {
      remotes::install_github('mattkcole/shinyaudio')
    }
    install.packages(package, repos = "http://cran.us.r-project.org")
  }
}

lapply(all_packages, require, character.only = TRUE)
```


# Presentation Overview  


```{r audio-intro}
shinyaudio::audio('./audio/Intro.mp3')
```


For the final presentation, I will be using the *Heart Disease UCI* dataset for Exploratory Data Analysis. This dataset is a tabular dataset. The dataset was found on the website *kaggle* at <https://www.kaggle.com/ronitf/heart-disease-uci/version/1>, but the set is from <https://archive.ics.uci.edu/ml/datasets/Heart+Disease>. The variables in the dataset that are of interest are:   
    * AGE: numerical  
    * SEX: categorical  
    * RESTING BLOOD PRESSURE: numerical  
    * SERUM CHOLESTORAL: numerical  
    * MAXIMUM HEART RATE: numerical  
    * EXERCISE INCLUDED ANGINA: categorical  
    * CHEST PAIN: categorical  
    * HEART DISEASE: categorical  
In addition, I will also go over how the presentation was setup using **rMarkdown**, **shinyApp**, and **embedded audio** with an example of downloading and loading required packages. The link to source code on *github* at <https://github.com/jmwinemiller/shiny-app>.  


```{r}
fluidPage(
  titlePanel("List of Packages"),
  fluidRow(column(
    12,
    tableOutput("packageList")
  ))
)

output$packageList <- renderTable(all_packages, colnames=F, spacing = 'xs')
```


```{r child='preprocessing.Rmd'}
```


```{r child='eda_plot.Rmd'}
```



