---
title: "EDA Presentation"
subtitle: "Heart Disease Among Factors of Health, Exercise induced angina, Heart Rates, and Demographic Information"
author: "Jordan Winemiller"
date: "14 May 2019"
output: 
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r packages, include=FALSE}
ip = installed.packages()[, 1]
ip <- names(unlist(ip))

required_packages = c(
  'remotes',
  'shiny',
  'ggplot2',
  'tidyverse',
  'dplyr',
  'summarytools',
  'ggiraph',
  'DT',
  'cowplot')

lapply(required_packages, require, character.only = TRUE)
```


# Presentation Overview  


For this presentation, I will be using the *Heart Disease UCI* dataset for Exploratory Data Analysis. This dataset is a tabular dataset. The dataset was found on the website *kaggle* at <https://www.kaggle.com/ronitf/heart-disease-uci/version/1>, but the set is from <https://archive.ics.uci.edu/ml/datasets/Heart+Disease>. The variables in the dataset that are of interest are:   
    * AGE: numerical  
    * SEX: categorical  
    * RESTING BLOOD PRESSURE: numerical  
    * SERUM CHOLESTORAL: numerical  
    * MAXIMUM HEART RATE: numerical  
    * EXERCISE INCLUDED ANGINA: categorical  
    * CHEST PAIN: categorical  
    * HEART DISEASE: categorical  
The link to source code on *github* at <https://github.com/jmwinemiller/shiny-app>.  


```{r}
fluidPage(
  titlePanel("List of Packages"),
  fluidRow(column(
    12,
    tableOutput("packageList")
  ))
)

output$packageList <- renderTable(required_packages, colnames=F, spacing = 'xs')
```


```{r child='preprocessing.Rmd'}
```


```{r child='eda_plot.Rmd'}
```


## Links  

Link to the presentation @ <https://jwinemiller.shinyapps.io/Presentation/>  
Link to the source code @ <https://github.com/jmwinemiller/shiny-app>  
Link to Data Tables <https://rstudio.github.io/DT/>  
